Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-04 paper/tex/results.tex
fixed minor grammar errors, added affiliation

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.  The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies.  This represents a very conservative estimate of the representative training sample size, and thus an approximate minimal error significance compared to ideal performance.  Deviations in the PIT histograms outside of this range show that significant biases are present for some codes.

@@

Close inspection of the extremes at PIT values of 0 and 1 reveal spikes in the first and last bin of the PIT histogram for some codes in Figure~\ref{fig:pitqq}, corresponding to ``catastrophic outliers'' where the true redshift lies outside of the support of the $p(z)$.  The catastrophic outlier rates are provided in Table~\ref{tab:pitoutlier}.
As expected, \trainz\ achieves precisely the 0.0002 value expected of an ideal PIT distribution.
\annz, \flexzboost, \lephare, and \metaphor\ have notably high catastrophic outlier rates $> 0.02$, exceeding 100 times the ideal PIT rate, meriting further investigation.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection in the differences in how each statistic weights the tails of the distribution.  Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz, none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

Figure~\ref{fig:pit_stats} displays the values of the KS, CvM, and AD test statistics calculated by comparing the PIT distribution and a uniform distribution $U(0, 1)$.  This plot highlights the relative rather than absolute numbers.  
\metaphor\ and \lephare\ perform well under the AD but poorly under the KS and CvM due to their high catastrophic outlier rates.
\annz\ and \flexzboost\  are the top scorers under these metrics of the PIT distribution.
\annz's strong performance can be attributed to an aspect of the training process in which training set galaxies with a PIT that more closely matches the percentiles of the DC1 training set's redshift distribution are upweighted; in effect, these quantile-based metrics were part of the algorithm itself that may or may not serve it well under more realistic experimental conditions.
Similar to what was done for the PIT histograms in Figure~\ref{fig:pitqq} we create bootstrap training samples of 30,000 galaxies for use with \trainz\ in order to estimate a conservative statistical floor that we would expect in real data.  No code reaches this idealized floor, indicating that all codes suffer some degradation from the ideal when employing their implicit priors, though \annz, \flexzboost, and \gpz\ are within a factor of two.

>>>>

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (i.~e.~ more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.
The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies, representing a very conservative estimate of the representative training sample size, and thus an approximate minimal error significance compared to ideal performance.
Deviations in the PIT histograms outside of this range show that significant biases are present for some codes.

@@

Close inspection of the extremes at PIT values of 0 and 1 reveal spikes in the first and last bin of the PIT histogram for some codes in Figure~\ref{fig:pitqq}, corresponding to catastrophic outliers where the true redshift lies outside of the support of the $p(z)$.
The catastrophic outlier rates are provided in Table~\ref{tab:pitoutlier}.
As expected, \trainz\ achieves precisely the 0.0002 value expected of an ideal PIT distribution.
\annz, \flexzboost, \lephare, and \metaphor\ have notably high catastrophic outlier rates $> 0.02$, exceeding 100 times the ideal PIT rate, meriting further investigation.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection in the differences in how each statistic weights the tails of the distribution.
Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz; none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

Figure~\ref{fig:pit_stats} highlights the relative values of the KS, CvM, and AD test statistics calculated by comparing the PIT distribution and a uniform distribution $U(0, 1)$.
\metaphor\ and \lephare\ perform well under the AD but poorly under the KS and CvM due to their high catastrophic outlier rates.
\annz\ and \flexzboost\  are the top scorers under these metrics of the PIT distribution.
\annz's strong performance can be attributed to an aspect of the training process in which training set galaxies with a PIT that more closely matches the percentiles of the DC1 training set's redshift distribution are upweighted; in effect, these quantile-based metrics were part of the algorithm itself that may or may not serve it well under more realistic experimental conditions.
Similar to what was done for the PIT histograms in Figure~\ref{fig:pitqq}, we create bootstrap training samples of 30,000 galaxies for use with \trainz\ in order to estimate a conservative statistical floor that we would expect in real data.
No code reaches this idealized floor, indicating that all codes suffer some degradation from the ideal when employing their implicit priors, though \annz, \flexzboost, and \gpz\ are within a factor of two.
